\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-08-31 Paper/Paper.tex
revise discussion.

	The combination of the Abnormity Models and the Diagnosis Model successfully improve the performance of the MAAM. The OCT Model and Fundus Model only have accuracies between 70\% and 80\% with the codominant abnormities method, with the Fundus Model having lower accuracy. The average accuracy of submodels in Stage D1 is still slightly lower than the OCT Model's accuracy, but it is already higher than the Fundus Model. Stage D2 makes the accuracy increase even further, with a 82\% accuracy without the codominant diseases method and a 89\% accuracy with the method.

	The Abnormity Models does not perform very well due to several reasons.

	There are often multiple abnormities on one image, and this is especially true for fundus images. Multiple abnormities increase the difficulty for the model to correctly extract and identify the abnormities.

	Also, the data used for training are collected from various online sources. The labeling criteria are different for different sources, so our data lack a uniform standard. Furthermore, some of the data selection are done by ourselves, but we do not have the expertise of ophthalmologists. As a result, our data is not very reliable.

	In addition, the size of our dataset is quite small and there is an imbalance between the number of images of different abnormities. In the OCT Model, the imbalance is partly neutralized by using Cycle-GAN to generate images. However, in the Fundus Model, we could only perform transformations to get more images, which may increase the model's tendency of being overfitting or make it hard for the model to extract the correct abnormities.

	The Diagnosis Model can increase the accuracy of the diagnosis for the following reasons.

	The Diagnosis Model performs two additional feature extracts based on the outputs of the Abnormity Models. In Stage D1, the severity levels of the diseases are extracted; and in Stage D2, the probabilities of diseases are extracted. Even though the Abnormity Models are not very accurate, for example, in discriminating similar abnormities, the Diagnosis Model can still extract key features and make a correct diagnosis.

	Additionally, in training the Diagnosis Model, we use the Abnormity-to-Disease Deduction Criteria to generate a new set of inputs and labels, which are reliable as long as the Criteria is correct. The Diagnosis Model is therefore trained on a relatively reliable set of data compared to the Abnormity Model.

@@

	Fundus 103262 imgs, 15 abnormities, 8 diseases \autocite{Son2023}

	TEXT: Strengths and weaknesses
	how to improve

>>>>

	There are some studies working on classifying OCT abnormities.  For examples, \citeauthor{leandro2023oct}'s model is trained on 10770 images (most images belong to multiple classes), classifies 8 abnormities, and has overall accuracy between 93\% and 99\% \autocite{leandro2023oct}. \citeauthor{li2019deep}'s model is trained on 21357 images, classifies 4 abnormities, and has overall accuracy 97.3\% \autocite{li2019deep}.  And there are some studies working on classifying fundus abnormities.  For example,  	\citeauthor{Son2023}'s model is trained on 103262 images, classifies 15 abnormities, and has a mean AUC of 0.980 \autocite{Son2023}. In comparison, our OCT Model is trained on 15632 images, classifies 11 abnormities, and has overall accuracy less than 80\%.  And our Fundus Model is trained on 1734 images, classifies 8 abnormities, and has a mean AUC of 0.909. As a matter of fact, our Abnormity Models are not satisfying in terms of performance.

	Our data are collected from various online sources and therefore lack a uniform standard. Furthermore, some of the data are labeled by ourselves, while we do not have the expertise of ophthalmologists. Moreover, our data is not sufficient. There is also an imbalance between the number of images of different abnormities. In the OCT Model, the imbalance is partly neutralized by using Cycle-GAN. However, in the Fundus Model, we could only perform transformations to generate more images, which may increase the model's tendency of being overfitting and make it hard for the model to extract the correct features. Also as mentioned before, in our model, there are often multiple abnormities on one image, which increase the difficulty to identify one specific abnormity correctly.

@@

	In MAAM, the Diagnosis Model improves the overall performance successfully. There are also some studies using similar framework. For example, \citeauthor{Son2023}'s diagnosis model classifies 8 diseases and has mean AUC 0.992\autocite{Son2023}. In comparison, our Diagnosis Model classifies 12 diseases and has mean AUC of 0.984 which is close to other studies.

	It is noted that the goal of MAAM is not to identify one specific disease.  It is developed for identifying all the potential diseases, which is different from other studies mentioned in this paper.  Therefore, we introduced codominant abnormities and codominant diseases, which buff up the performances. Moreover, the Diagnosis Model performs two additional feature extractions. While the Abnormity Models only have accuracies between 70\% and 80\%, after we extracted the features of severity levels of diseases in Stage D1, the average accuracy increases. And after we extracted the features of disease in Stage D2, the accuracy keep on increasing up to a satisfying level. These two stages enhance the performance of the Abnormity Models and make the features of the diseases more distinct.	Also, in training the Diagnosis Model, we use the Abnormity-to-Disease Deduction Criteria to generate ground truth, which is reliable even without involving ophthalmologists.
